%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                        %
%      This file is part of the 'lilyglyphs' LaTeX package.              %
%                                ==========                              %
%                                                                        %
%              https://github.com/openlilylib/lilyglyphs                 %
%               http://www.openlilylib.org/lilyglyphs                    %
%                                                                        %
%  Copyright 2012-2013 Urs Liska and others, ul@openlilylib.org          %
%                                                                        %
%  'lilyglyphs' is free software: you can redistribute it and/or modify  %
%  it under the terms of the LaTeX Project Public License, either        %
%  version 1.3 of this license or (at your option) any later version.    %
%  You may find the latest version of this license at                    %
%               http://www.latex-project.org/lppl.txt                    %
%  more information on                                                   %
%               http://latex-project.org/lppl/                           %
%  and version 1.3 or later is part of all distributions of LaTeX        %
%  version 2005/12/01 or later.                                          %
%                                                                        %
%  This work has the LPPL maintenance status 'maintained'.               %
%  The Current Maintainer of this work is Urs Liska (see above).         %
%                                                                        %
%  This work consists of the files listed in the file 'manifest.txt'     %
%  which can be found in the 'license' directory.                        %
%                                                                        %
%  This program is distributed in the hope that it will be useful,       %
%  but WITHOUT ANY WARRANTY; without even the implied warranty of        %
%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.                  %
%                                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[oneside,11pt]{article}
\usepackage{lilyglyphsStyle}
\usepackage{lilyglyphsManualFonts}

\newcommand{\superscript}[1]{{\addfontfeatures{VerticalPosition=Superior}#1}}
\linespread{1.1}

% make the glyphs lighter
\lilyOpticalSize{26}

\begin{document}
\begin{center}
{ \Huge \lilyglyphs }

\bigskip
{ \Large Urs Liska }

\emph{September 2013} 

\end{center}

\bigskip

You are authoring text documents about music, maybe you're a musicologist, teacher, or composer?
You are preparing such documents for publication and have always missed the ability to print sentences like this one?

\begin{quote}
In m.\,24 the \decrescHairpin{} lasts from the 2\superscript{nd} \halfNote{} to the \lilyDynamics{sf} on the 11\superscript{th} \semiquaverDown[raise=-.5].
\end{quote}

With the new package \lilyglyphs{} you can easily insert the notational elements of LilyPond%
\footnote{\url{http://www.lilypond.org}}
in your text documents.
Accidentals like \flat{} or \sharp, but also articulation scripts (\hspace{.65ex}\fermata{}) and time signatures such as \lilyTimeCHalf{} or \lilyTimeSignature{5\,+\,7}{8} are readily available.
But you can also insert arbitrary notational constructs like this \fancyExample{} mockup example into your text or even make scanned images available as “characters”.
This package may greatly extend your typographical options when authoring critical reports or analytical essays.

One thing that sets \lilyglyphs{} apart from other solutions I had investigated is that one isn't restricted to a set of predefined symbols but is able to print \emph{any notation} that can be realized with LilyPond. 

\footnotesize
The other nice thing is that the glyphs \halfNoteRest{} scale well with the surrounding font size, 
\large making it easy \halfNoteRest{} to incorporate them into continuous text.
\normalsize By default the glyphs scale automatically but they can also be scaled \clefF[scale=.4] manually, either individually or document-wise \clefG[scale=1.5,raise=-3.1].

\medskip
This flexibility has a “price”, though: You will have to change your mind-set and start using plain text based tools, \LaTeX{}%
\footnote{\url{http://www.latex-project.org}}
in particular.
But if the above examples whet your appetite and match your professional needs you should really consider giving it a serious try -- it's all Free Software anyway.
You may find reading my essay on the advantages of plain text toolchains rewarding too%
\footnote{\url{http://lilypondblog.org/2013/07/plain-text-files-in-music/}}.
 
For more information you may visit \lilyglyphs' project homepage \url{http://openlilylib.org/lilyglyphs} or contact us through \href{mailto:info@openlilylib.org}{info@openlilylib.org}.

\end{document}